---
title: "linreg_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Linear regression model has been created
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab4Linreg)
mod_object <- linreg(formula = Petal.Length ~ Species , data = iris)
```


#Introduction

This document provides documentation for the linreg class which is tested with iris data set a tool for performing multiple linear regression analysis in R. The linreg class simplifies the process of fitting linear regression models and presenting the results of the statistics.


# resid() 
#It returns the vector of residuals.
```{r, eval=TRUE, include=TRUE}
mod_object$resid()
```

# pred() 
#It returns the predicted values.
```{r, eval=TRUE, include=TRUE, output.lines=4}
mod_object$pred()
```


# coef() 
#It returns the coefficients.
```{r, eval=TRUE, include=TRUE}
mod_object$coef()
```

# summary() 
#It presents the coefficients with their standard error, p-values and t-values and the estimatation of σˆ and the degrees of the freedom.
```{r, eval=TRUE, include=TRUE}
mod_object$summary()
```


# Print() 
#It prints out the coefficients and coefficient names
```{r, eval=TRUE, include=TRUE}
mod_object$print()
```


#Plot()
#It generates the plots using ggplot2
```{r, eval=TRUE, include=TRUE}
library(ggplot2)
plot_results=mod_object$plot()
```


#1st plot
#It shows the first plot with the residuals and the fitted values.
```{r, eval=TRUE, include=TRUE}
plot_results[1]
```


#2nd plot
#It shows the second plot with the square root of the standardized residuals and the fitted values.
```{r, eval=TRUE, include=TRUE}
plot_results[2]
```






